---
title: "Developing Data Projects Final Project"
author: "Sophia"
date: "12/10/2021"
output: 
        ioslides_presentation:
        keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Coursera Peer Graded Assignment Reproducible Pitch

- The details of the assignment is from the web adress:
        
https://www.coursera.org/learn/data-products/peer/tMYrn/course-project-shiny-application-and-reproducible-pitch

- The shiny application and the link is :
        
https://sophiaqy.shinyapps.io/mpgapp/
        
- The codes of server.R and ui.R are on the link:
        
https://github.com/SophiaQY/DDP_Final_Project

## Data set and introduction to the App

In this project, we investigated the relationship between Miles per Gallon (mpg) and Horse Power (hp)
```{r}
head(mtcars)
```
This app plot a figure showing mpg vs hp, simply select data points using your mouse, then a regression model will be applied to the select data. It will return with the slope and intercept of the regression model, and you have the option to show or hide the regression line with the checkbox. 


## Code for ui.R


library(shiny)

shinyUI(fluidPage(

        titlePanel("Visualize models"),
        sidebarLayout(
                sidebarPanel(
                        h4("Slope and Intercept"),
                        textOutput("SlopeOut"),
                        textOutput("intOut"),
                        checkboxInput("showModel", "Show/Hide model", value = TRUE),
                        hr(),
                        helpText("1. Use your mouse to select a set of data points to see the fitted model of mpg by hp."),
                        hr(),
                        helpText("2. Show/Hide model will show/hide a regression line of the selected data.")
                ),
                mainPanel(
                        plotOutput("plot1", brush=brushOpts(
                                id="brush1"
                        ))
                )
        )
))

## Code for server.R

shinyServer(function(input, output){
        
        model <- reactive({
                brushed_data <- brushedPoints(mtcars, input$brush1,
                                              xvar = "hp", yvar = "mpg")
                if(nrow(brushed_data)<2){
                        return(NULL)
                }
                lm(mpg ~ hp, data= brushed_data)
        })
        
        output$slopeOut <- renderText({
                if(is.null(model())){
                        "No Model Found"
                } else {
                        model()[[2]]
                }
        })
        
        output$intOut <- renderText({
                if(is.null(model())){
                        "No Model Found"
                } else {
                        model()[[1]]
                }
        })
        
        output$plot1 <- renderPlot({
                plot(mtcars$hp, mtcars$mpg, xlab = "Horse Power", ylab = "Miles per Gallon",
                     main = "MPG VS horse power", cex=1.5, pch=16, bty="n")
                if(input$showModel){
                        abline(model(), col="blue", lwd=2)
                }
        })
})


